DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-20 paper/appendix.tex
removed the loss figure.

\begin{figure*}[t]
  \centering
  \includegraphics[width=.9\textwidth]{figs/TrainingLoss}
  \caption{Change in loss value throughout training.}
  \label{fig:modelloss}
\end{figure*}

@@

In the first method, we trained the neural network model across a set 
of 30 completed runs on the track seen in Figure~\ref{fig:track2} by a
human pilot. Half of the runs saw the car driving one way along the
track, while the remaining half were of the car driving in the
opposite direction on the track.
In total, we collected 2,556 frames for training and 2,609 
frames for validation.
The weights of the network are initialized using a Xavier
initializer~\cite{Glorot2010}, which is known to provide better
initial values than the random weight assignment method.
In each training step, we use a batch
size of 100 frames, which are randomly selected among all the
collected training images, to optimize the network.
We repeat this across 2,000 training steps.
%% When a model was trained
%% with the  aformentioned data, the training loss was 0.0188 and the
%% validation  loss was 0.0132.
Figure~\ref{fig:modelloss} shows the change of the loss value over the
course of model training.

@@

We plan to investigate ways to achieve better prediction accuracy
in training the network. We also plan to evaluate different RC
car platforms that have different steering mechanisms to see their
impact to the control performance.

>>>>

%% \begin{figure*}[t]
%%   \centering
%%   \includegraphics[width=.9\textwidth]{figs/TrainingLoss}
%%   \caption{Change in loss value throughout training.}
%%   \label{fig:modelloss}
%% \end{figure*}

@@

In the first method, we trained the neural network model across a set 
of 30 completed runs on the track seen in Figure~\ref{fig:track2} by a
human pilot. Half of the runs saw the car driving one way along the
track, while the remaining half were of the car driving in the
opposite direction on the track.
In total, we collected 2,556 frames for training and 2,609 
frames for validation.
The weights of the network are initialized using the Xavier
initializer~\cite{Glorot2010}, which is known to perform better
than a random weight assignment.
In each training step, we use a batch
size of 100 frames, which are randomly selected among all the
collected training images, to optimize the network.
We repeat this across 2,000 training steps.
%% When a model was trained
%% with the  aformentioned data, the training loss was 0.0188 and the
%% validation  loss was 0.0132.
%% Figure~\ref{fig:modelloss} shows the change of the loss value over the
%% course of model training.

@@

%% We plan to investigate ways to achieve better prediction accuracy
%% in training the network. We also plan to evaluate different RC
%% car platforms that have different steering mechanisms to see their
%% impact to the control performance.
